### 2022-11-11 dissertation/chapters/08-results.tex
🚧 (results): Replotting figures

\noindent
All the required background information on all the elements relevant to the empirical process have been presented in Chapters~\ref{chap:anns}-\ref{chap:probability}. The proposed \acf{BHH} was presented in Chapter~\ref{chap:bhh} and the design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}. The methodology presented a number of experiments to conduct, including a case study on the behaviour of the \acs{BHH} during training, and a comparison to the performance of state-of-the-art, standalone, low-level heuristics. The methodology also defined a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.

Finally, this chapter provides the outcome of these empirical processes and provides results on all the experiments that have been conducted. Detailed discussions follow on the outcomes of each experiment. Discussions are accompanied by figures and plots to help provide visual aid for the discussions. All experiments and discussions also provide the outcome of the statistical analysis of the results. The remainder of the chapter is structured as follows.

@@

      \item \textbf{Section \ref{sec:results:bhh_vs_low_level_heuristics}} provides the results of the performance of the \acs{BHH} compared to individual low-level heuristics as it relates to all datasets. Three variants of the \acs{BHH} are included in these results. These include the baseline configuration, as well as a configuration that only includes gradient-based heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes meta-heuristics in the \index{heuristic pool}heuristic pool.

@@

      \item \textbf{Section \ref{sec:results:computational_req}} provides a brief discussion on the practical application of the \acs{BHH} to real-world problems.

      \item \textbf{Section \ref{sec:results:overview}} provides an overview of all the results for all the empirical tests, followed by a brief discussion on the overall performance of the \acs{BHH}.

      \item \textbf{Section \ref{sec:results:overview}} provides a brief summary of the chapter.
\end{itemize}

>>>>

\noindent
All the required background information on all the elements relevant to the empirical process have been presented in Chapters~\ref{chap:anns}-\ref{chap:probability}. The proposed \acf{BHH} was presented in Chapter~\ref{chap:bhh} and the design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}. The methodology presented a number of experiments to conduct, including a case study on the behaviour of the \acs{BHH} during training, and a comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics. The methodology also defined a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.

Finally, this chapter provides the outcome of these empirical processes and provides results on all the experiments that have been conducted. Detailed discussions follow on the outcomes of each experiment. Discussions are accompanied by figures and plots to help provide visual aid for the discussions. The output of the statistical analysis that yielded the results presented in the chapter is provided in Appendix~\ref{app:statistical_analysis}. The remainder of the chapter is structured as follows.

@@

      \item \textbf{Section \ref{sec:results:bhh_vs_low_level_heuristics}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics as it relates to all datasets. Three variants of the \acs{BHH} are included in these results. These include the baseline configuration, as well as a configuration that only includes gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes meta-heuristics in the \index{heuristic pool}heuristic pool.

@@

      \item \textbf{Section \ref{sec:results:practical_applications}} provides a brief discussion on the practical application of the \acs{BHH} to real-world problems.

      \item \textbf{Section \ref{sec:results:summary}} provides a brief summary of the chapter.
\end{itemize}

\section{Behavioural Case Study}\label{sec:results:case_study}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% METRICS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_loss.pdf}
      \caption{The average training loss over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:train_loss}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_loss.pdf}
      \caption{The average test loss over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:test_loss}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_accuracy.pdf}
      \caption{The average training accuracy over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:train_accuracy}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_accuracy.pdf}
      \caption{The average test accuracy over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:test_accuracy}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS ALPHAS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
      \caption{The average value of the concentration parameter $\alpha_{0}$ (\acs{SGD}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:alpha:0}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
      \caption{The average value of the concentration parameter $\alpha_{6}$ (\acs{Adam}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:alpha:6}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
      \caption{The average value of the concentration parameter $\alpha_{7}$ (\acs{PSO}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:alpha:7}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
      \caption{The average value of the concentration parameter $\alpha_{8}$ (\acs{GA}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:alpha:8}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS THETAS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
      \caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{0}$ (\acs{SGD}), given concentration parameter $\alpha_{0}$, sampled from the probability distribution $P(\theta_{0} \vert \alpha_{0})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:theta:0}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
      \caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{6}$ (\acs{Adam}), given concentration parameter $\alpha_{6}$, sampled from the probability distribution $P(\theta_{6} \vert \alpha_{6})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:theta:6}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
      \caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{7}$ (\acs{PSO}), given concentration parameter $\alpha_{7}$, sampled from the probability distribution $P(\theta_{7} \vert \alpha_{7})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:theta:7}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
      \caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{8}$ (\acs{GA}), given concentration parameter $\alpha_{8}$, sampled from the probability distribution $P(\theta_{8} \vert \alpha_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:theta:8}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS P_H (Priors)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
      \caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the probability of the selection probability, denoted by $\theta_{0}$, sampled from the prior selection probability distribution $P(h_{0} \vert \theta_{0})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_H:0}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
      \caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the probability of the selection probability, denoted by $\theta_{6}$, sampled from the prior selection probability distribution $P(h_{6} \vert \theta_{6})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_H:6}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
      \caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the probability of the selection probability, denoted by $\theta_{7}$, sampled from the prior selection probability distribution $P(h_{7} \vert \theta_{7})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_H:7}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
      \caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the probability of the selection probability, denoted by $\theta_{8}$, sampled from the prior selection probability distribution $P(h_{8} \vert \theta_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_H:8}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS P_HgEC (Posterior)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
      \caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{0} \vert \theta_{0} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_HgEC:0:0}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
      \caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{6} \vert \theta_{6} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_HgEC:0:6}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
      \caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{7} \vert \theta_{7} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_HgEC:0:7}
\end{figure}

\begin{figure}[htpb]
      \centering
      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
      \caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{8} \vert \theta_{8} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_HgEC:0:8}
\end{figure}

\section{BHH vs. Low-Level Heuristics}\label{sec:results:bhh_vs_low_level_heuristics}

% Table generated by Excel2LaTeX from sheet 'results - test - loss'
\begin{table}[htbp]
      \centering
      \caption{Empirical results showcasing average test loss and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs, at the last epoch.}
      \label{tab:results:standalone:metrics:test_loss}%
      \par\bigskip
      \resizebox{\textwidth}{!}{
            \begin{tabular}{rlccc|c|c|c|c|c|ccccc}
                  epoch                                                                          & 30                 &                                                                                &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
                                                                                                 &                    &                                                                                &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
                                                                                                 &                    & \multicolumn{1}{l}{\textbf{heuristic}}                                         &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
                  \cmidrule{3-3}\cmidrule{6-6}\cmidrule{8-8}\cmidrule{10-10}    \textbf{dataset} & \textbf{statistic} & \textbf{adagrad}                                                               & \textbf{adam}                                                                  & \textbf{nag}                                                                   & \textbf{bhh\_gd}                                & \textbf{rmsprop}                                                               & \textbf{bhh\_all}                               & \textbf{adadelta}                                                              & \textbf{bhh\_mh}                                & \textbf{ga}                                     & \textbf{sgd}                                    & \textbf{pso}                                    & \textbf{momentum}                               & \textbf{de}                                     \\
                  \midrule
                  abalone                                                                        & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
                                                                                                 & avg                & \cellcolor[rgb]{ .506,  .776,  .486}1.967785                                   & \cellcolor[rgb]{ .494,  .773,  .486}1.965134827                                & \cellcolor[rgb]{ .765,  .851,  .502}2.0156043                                  & \cellcolor[rgb]{ .749,  .847,  .502}2.012517173 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{1.94553315}  & \cellcolor[rgb]{ 1,  .922,  .518}2.058704583    & \cellcolor[rgb]{ .788,  .859,  .502}2.019921077                                & \cellcolor[rgb]{ .996,  .827,  .502}2.29420573  & \cellcolor[rgb]{ .984,  .612,  .459}2.81545685  & \cellcolor[rgb]{ .992,  .773,  .49}2.42804241   & \cellcolor[rgb]{ .98,  .522,  .443}3.038417873  & \cellcolor[rgb]{ .992,  .745,  .486}2.494169393 & \cellcolor[rgb]{ .973,  .412,  .42}3.295858177  \\
                                                                                                 & std                & 0.031577789                                                                    & 0.034949967                                                                    & 0.034657443                                                                    & 0.068121366                                     & 0.035183664                                                                    & 0.087594488                                     & 0.034405331                                                                    & 0.055085207                                     & 0.055148148                                     & 0.028810924                                     & 0.293755503                                     & 0.029086341                                     & 0.016489872                                     \\
                  adult                                                                          & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
                                                                                                 & avg                & \cellcolor[rgb]{ 1,  .922,  .518}0.346737798                                   & \cellcolor[rgb]{ 1,  .922,  .518}0.38233353                                    & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.313320884} & \cellcolor[rgb]{ .788,  .859,  .502}0.335180995 & \cellcolor[rgb]{ .933,  .902,  .514}0.343292783                                & \cellcolor[rgb]{ .973,  .412,  .42}586.2065996  & \cellcolor[rgb]{ .467,  .765,  .486}0.317677033                                & \cellcolor[rgb]{ 1,  .922,  .518}0.363543899    & \cellcolor[rgb]{ 1,  .922,  .518}0.392047161    & \cellcolor[rgb]{ .388,  .745,  .482}0.313329677 & \cellcolor[rgb]{ 1,  .922,  .518}1.217724345    & \cellcolor[rgb]{ .388,  .745,  .482}0.313444396 & \cellcolor[rgb]{ 1,  .922,  .518}0.639695856    \\
                                                                                                 & std                & 0.003704238                                                                    & 0.018067239                                                                    & 0.000510377                                                                    & 0.043628962                                     & 0.014659665                                                                    & 1261.204704                                     & 0.005277776                                                                    & 0.020803371                                     & 0.020086997                                     & 0.000411017                                     & 0.496591684                                     & 0.0003947                                       & 0.042558869                                     \\
                  air quality                                                                    & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
                                                                                                 & avg                & \cellcolor[rgb]{ .651,  .82,  .494}0.256871193                                 & \cellcolor[rgb]{ .827,  .871,  .506}0.260623969                                & \cellcolor[rgb]{ .647,  .82,  .494}0.256829053                                 & \cellcolor[rgb]{ 1,  .922,  .518}0.264177871    & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.251334045} & \cellcolor[rgb]{ .996,  .827,  .502}0.272859303 & \cellcolor[rgb]{ .647,  .82,  .494}0.256781683                                 & \cellcolor[rgb]{ .976,  .914,  .514}0.263703859 & \cellcolor[rgb]{ .996,  .792,  .494}0.275862527 & \cellcolor[rgb]{ .988,  .69,  .475}0.285172782  & \cellcolor[rgb]{ .984,  .608,  .459}0.292264593 & \cellcolor[rgb]{ .984,  .604,  .459}0.292851261 & \cellcolor[rgb]{ .973,  .412,  .42}0.309698115  \\
                                                                                                 & std                & 0.007475522                                                                    & 0.008912099                                                                    & 0.005955119                                                                    & 0.011452365                                     & 0.007814891                                                                    & 0.016310047                                     & 0.00630808                                                                     & 0.007306605                                     & 0.008162884                                     & 0.014769128                                     & 0.022648597                                     & 0.016417541                                     & 0.017044223                                     \\
                  bank                                                                           & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
                                                                                                 & avg                & \cellcolor[rgb]{ .459,  .765,  .486}0.209641222                                & \cellcolor[rgb]{ .4,  .745,  .482}0.206461621                                  & \cellcolor[rgb]{ .588,  .8,  .49}0.2164275                                     & \cellcolor[rgb]{ .588,  .8,  .49}0.21643132     & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.205779476} & \cellcolor[rgb]{ 1,  .886,  .514}0.245610465    & \cellcolor[rgb]{ .627,  .812,  .494}0.218599386                                & \cellcolor[rgb]{ .996,  .839,  .502}0.256171151 & \cellcolor[rgb]{ .988,  .686,  .475}0.28813827  & \cellcolor[rgb]{ 1,  .922,  .518}0.238179998    & \cellcolor[rgb]{ .973,  .412,  .42}0.345448185  & \cellcolor[rgb]{ 1,  .922,  .518}0.238550439    & \cellcolor[rgb]{ .976,  .424,  .424}0.343699166 \\
                                                                                                 & std                & 0.004750498                                                                    & 0.004040969                                                                    & 0.005944898                                                                    & 0.004889433                                     & 0.005654034                                                                    & 0.064531685                                     & 0.003821749                                                                    & 0.010550504                                     & 0.012801143                                     & 0.005568018                                     & 0.033990143                                     & 0.004820977                                     & 0.028120079                                     \\
                  bike                                                                           & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
                                                                                                 & avg                & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.045805387} & \cellcolor[rgb]{ .592,  .804,  .494}0.068179412                                & \cellcolor[rgb]{ .882,  .886,  .51}0.099539486                                 & \cellcolor[rgb]{ .467,  .765,  .486}0.054496914 & \cellcolor[rgb]{ 1,  .922,  .518}0.112259627                                   & \cellcolor[rgb]{ .565,  .796,  .49}0.065136647  & \cellcolor[rgb]{ .588,  .8,  .49}0.06793708                                    & \cellcolor[rgb]{ 1,  .902,  .514}0.11787523     & \cellcolor[rgb]{ .992,  .761,  .486}0.153095534 & \cellcolor[rgb]{ .992,  .733,  .482}0.159868436 & \cellcolor[rgb]{ .992,  .773,  .49}0.150273084  & \cellcolor[rgb]{ .992,  .725,  .482}0.161397393 & \cellcolor[rgb]{ .973,  .412,  .42}0.239867227  \\
                                                                                                 & std                & 0.001725608                                                                    & 0.068117237                                                                    & 0.001754469                                                                    & 0.005239285                                     & 0.103490928                                                                    & 0.019626763                                     & 0.002076596                                                                    & 0.005954748                                     & 0.005079692                                     & 0.002759                                        & 0.025177188                                     & 0.003354245                                     & 0.039791214                                     \\
                  car                                                                            & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
                                                                                                 & avg                & \cellcolor[rgb]{ .729,  .843,  .502}0.202726327                                & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.09724452}  & \cellcolor[rgb]{ .867,  .882,  .51}0.245363623                                 & \cellcolor[rgb]{ .62,  .812,  .494}0.16895294   & \cellcolor[rgb]{ .408,  .749,  .482}0.103937737                                & \cellcolor[rgb]{ .58,  .8,  .49}0.15718728      & \cellcolor[rgb]{ 1,  .922,  .518}0.285888989                                   & \cellcolor[rgb]{ .992,  .733,  .482}0.489062582 & \cellcolor[rgb]{ .98,  .502,  .439}0.737354357  & \cellcolor[rgb]{ .98,  .533,  .443}0.703539757  & \cellcolor[rgb]{ .988,  .667,  .471}0.563173207 & \cellcolor[rgb]{ .98,  .506,  .439}0.73217904   & \cellcolor[rgb]{ .973,  .412,  .42}0.833160108  \\
                                                                                                 & std                & 0.018356416                                                                    & 0.023870777                                                                    & 0.028744869                                                                    & 0.025441117                                     & 0.031133074                                                                    & 0.033710554                                     & 0.027353972                                                                    & 0.076505599                                     & 0.062600847                                     & 0.052091474                                     & 0.157928484                                     & 0.042705727                                     & 0.074182791                                     \\
                  diabetic                                                                       & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
                                                                                                 & avg                & \cellcolor[rgb]{ .694,  .831,  .498}0.889537739                                & \cellcolor[rgb]{ 1,  .898,  .514}0.919339482                                   & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.880898965} & \cellcolor[rgb]{ .98,  .914,  .514}0.897587026  & \cellcolor[rgb]{ .918,  .894,  .51}0.895749019                                 & \cellcolor[rgb]{ .973,  .412,  .42}1.298319185  & \cellcolor[rgb]{ .49,  .773,  .486}0.883864405                                 & \cellcolor[rgb]{ 1,  .902,  .518}0.913694494    & \cellcolor[rgb]{ .996,  .843,  .506}0.961291775 & \cellcolor[rgb]{ .976,  .914,  .514}0.897429714 & \cellcolor[rgb]{ .996,  .835,  .502}0.966103049 & \cellcolor[rgb]{ 1,  .922,  .518}0.898038783    & \cellcolor[rgb]{ .988,  .694,  .475}1.077362637 \\
                                                                                                 & std                & 0.004272255                                                                    & 0.00981794                                                                     & 0.003758597                                                                    & 0.010748722                                     & 0.004045488                                                                    & 0.659754133                                     & 0.004759234                                                                    & 0.008388702                                     & 0.00657199                                      & 0.003551413                                     & 0.016450474                                     & 0.002801135                                     & 0.0391395                                       \\
                  fish toxicity                                                                  & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
                                                                                                 & avg                & \cellcolor[rgb]{ .588,  .8,  .49}0.09908239                                    & \cellcolor[rgb]{ .451,  .761,  .482}0.097196901                                & \cellcolor[rgb]{ .831,  .871,  .506}0.10233624                                 & \cellcolor[rgb]{ 1,  .91,  .518}0.105584544     & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.096326802} & \cellcolor[rgb]{ 1,  .922,  .518}0.104598099    & \cellcolor[rgb]{ .773,  .855,  .502}0.101567158                                & \cellcolor[rgb]{ .976,  .914,  .514}0.104293618 & \cellcolor[rgb]{ 1,  .863,  .506}0.109342435    & \cellcolor[rgb]{ .976,  .475,  .435}0.139280655 & \cellcolor[rgb]{ 1,  .855,  .506}0.109946059    & \cellcolor[rgb]{ .973,  .412,  .42}0.144088336  & \cellcolor[rgb]{ .992,  .733,  .482}0.119344204 \\
                                                                                                 & std                & 0.008463336                                                                    & 0.006948088                                                                    & 0.007611236                                                                    & 0.008228438                                     & 0.008021585                                                                    & 0.008136956                                     & 0.008882708                                                                    & 0.00895412                                      & 0.008990894                                     & 0.012326524                                     & 0.012481736                                     & 0.012407706                                     & 0.0130782                                       \\
                  forest fires                                                                   & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
                                                                                                 & avg                & \cellcolor[rgb]{ 1,  .922,  .518}0.064321917                                   & \cellcolor[rgb]{ .557,  .792,  .49}0.052658676                                 & \cellcolor[rgb]{ .851,  .878,  .506}0.05923886                                 & \cellcolor[rgb]{ .824,  .871,  .506}0.058617148 & \cellcolor[rgb]{ 1,  .922,  .518}0.062552555                                   & \cellcolor[rgb]{ 1,  .89,  .514}0.080966845     & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.048831474} & \cellcolor[rgb]{ .976,  .914,  .514}0.06209696  & \cellcolor[rgb]{ .553,  .792,  .49}0.05260701   & \cellcolor[rgb]{ .992,  .722,  .482}0.180571383 & \cellcolor[rgb]{ 1,  .914,  .518}0.069210426    & \cellcolor[rgb]{ .992,  .706,  .478}0.188476672 & \cellcolor[rgb]{ .973,  .412,  .42}0.359831599  \\
                                                                                                 & std                & 0.039911806                                                                    & 0.039243672                                                                    & 0.031685801                                                                    & 0.034163415                                     & 0.039170629                                                                    & 0.069099845                                     & 0.032095867                                                                    & 0.038470671                                     & 0.025957821                                     & 0.008365929                                     & 0.047244856                                     & 0.010081381                                     & 0.089999905                                     \\
                  housing                                                                        & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
                                                                                                 & avg                & \cellcolor[rgb]{ .518,  .78,  .486}0.088925893                                 & \cellcolor[rgb]{ .404,  .749,  .482}0.08481865                                 & \cellcolor[rgb]{ .612,  .808,  .494}0.092269667                                & \cellcolor[rgb]{ .69,  .831,  .498}0.095072459  & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.08422333}  & \cellcolor[rgb]{ .663,  .824,  .498}0.094078934 & \cellcolor[rgb]{ 1,  .922,  .518}0.105999965                                   & \cellcolor[rgb]{ 1,  .867,  .51}0.116883814     & \cellcolor[rgb]{ .996,  .812,  .498}0.127851649 & \cellcolor[rgb]{ .984,  .576,  .455}0.173521216 & \cellcolor[rgb]{ .992,  .722,  .482}0.145240159 & \cellcolor[rgb]{ .984,  .588,  .455}0.171302372 & \cellcolor[rgb]{ .973,  .412,  .42}0.205724786  \\
                                                                                                 & std                & 0.012490666                                                                    & 0.011213172                                                                    & 0.015551947                                                                    & 0.014823695                                     & 0.014924594                                                                    & 0.017302471                                     & 0.018700331                                                                    & 0.019460369                                     & 0.020192262                                     & 0.022837541                                     & 0.029813905                                     & 0.017916976                                     & 0.036445189                                     \\
                  iris                                                                           & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
